---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

```{r, include = FALSE}
# library(bootcorci)
devtools::load_all()
library(ggplot2)
```

# bootcorci

<!-- badges: start -->
<!-- badges: end -->

The goal of `bootcorci` is to provide bootstrap methods to compute confidence intervals for correlation coefficients and their differences. All the functions have been adapted from Rand Wilcox's [functions](http://dornsife.usc.edu/labs/rwilcox/software/). The functions in the package have been standardised in their names, inputs and outputs. When two versions of the same function existed to handle separately Pearson's correlation and robust correlations, the two versions have been merged. Simplified versions of the correlation functions have been created to speed up the bootstrap analyses. All the bootstrap functions return the bootstrap samples.

## Functions

### Correlation functions

|name|purpose|
|-----|-----|
|test|test|

### Bootstrap functions

|name|purpose|
|-----|-----|
|test|test|

## Installation

You can install `bootcorci` from GitHub by using `devtools`:
```{r GitHub install, eval = FALSE}
install.packages("devtools")
devtools::install_github("GRousselet/bootcorci")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
# library(bootcorci)
## basic example code
```


